---
title: "Toeplitz DGP"
output: html_document
date: "2023-06-24"
---
```{r package}
library(TSclust)
library(cluster)
library(factoextra)
library(MASS)
```

The following function is used to generate the sample values.

```{r ty1}
generate1 <- function(mu1,n,p)
{
  Sigma1 <- matrix(0,p,p)
  for(i in 1:p)
  {
    for(j in 1:p)
    {
      Sigma1[i,j] <- 0.15^abs(i-j)
    }
  }
  X <- matrix(0,nrow=p,ncol=n)
  for(i in 1:n)
  {
    X[,i] <- mvrnorm(1,mu=mu1,Sigma=Sigma1)
  }
  return(X)
}
```

```{r tyr3}



matfull3 <- function(n,prev)
{
  b <- 0
  x <- numeric()
  n1 <- which(grpnew==n)
  for(i in 1:(length(n1)-1))
  {
  
    a <- b+1
    
    b <- a+(length(n1)-i)-1
    
    x <- rbind(x,c(rep(0,i-1),rep(1,1),prev[a:b]))
  }
  x <- rbind(x,c(rep(0,length(n1)-1),rep(1,1)))
  return(x)
}
matfull4 <- function(n,prev)
{
  b <- 0
  x <- numeric()
  n1 <- which(grpnew==n)
  for(i in 1:(length(n1)-1))
  {
  
    a <- b+1
    
    b <- a+(length(n1)-i)-1
    
    x <- cbind(x,c(rep(0,i),prev[a:b]))
  }
  x <- cbind(x,c(rep(0,length(n1))))
  return(x)
}


theta4 <- function(Y,X,tol=1e-5,gamma)      #function for final value of theta
{
  distance <- tol + 1
  iter <- 0
  
  fubc <- function(Y,X,gamma)        #function for initial value of theta 
  {
    a <- sign(t(Y)%*%X)
    y <- ifelse(as.numeric(((abs(t(Y)%*%X)-gamma)/(t(X)%*%X))>0),(abs(t(Y)%*%X)-gamma)/(t(X)%*%X),0)
    a1 <- a*y
    return(a)
  }
  
  
  theta <- numeric()
  
  for(i in 1:ncol(X))
  {
    theta[i] <- fubc(Y,X[,i],gamma)
  }
  
  distance <- tol + 1
  iter <- 0

  
  while(distance > tol)
  {
    iter <- iter + 1
    
    
    previous <- theta
    
    
  for(i in 1:ncol(X))
  {
  
    
      b <- sign(((t(Y-X%*%previous)%*%X[,i])/(t(X[,i])%*%X[,i]))+previous[i])
      y1 <- ifelse(as.numeric(abs(((t(Y-X%*%previous)%*%X[,i])/(t(X[,i])%*%X[,i]))+previous[i])-(gamma/(t(X[,i])%*%X[,i]))>0),abs(((t(Y-X%*%previous)%*%X[,i])/(t(X[,i])%*%X[,i]))+previous[i])-(gamma/(t(X[,i])%*%X[,i])),0)
      theta[i] <- b*y1
    }
    distance <- norm(previous-theta,"2")
    distance
    
  }
  return(theta)
}
```


```{r next114}
newfunc <- function(n,p,c,gamma)
{
   gam <- gamma
   theta2 <- list()
   mat2 <- list()
   for(n in 1:c)
   {
     
      n2 <- which(grpnew==n)
      if(length(n2) != 1)
      {
        tol <- 1e-5
        distance <- 1 + tol
        iter <- 0 

        value1 <- t(value) 
        val <- value1[,n2]
        matfull <- function(prev)
  {
  b <- 0
  x <- numeric()
  for(i in 1:(ncol(val)-1))
  {
  
    a <- b+1
    
    b <- a+(ncol(val)-i)-1
    
    x <- rbind(x,c(rep(0,i-1),rep(1,1),prev[a:b]))
  }
  x <- rbind(x,c(rep(0,ncol(val)-1),rep(1,1)))
  return(x)
        }
        matfull3 <- function(n,prev)
{
  b <- 0
  x <- numeric()
  n1 <- which(grpnew==n)
  for(i in 1:(length(n1)-1))
  {
  
    a <- b+1
    
    b <- a+(length(n1)-i)-1
    
    x <- rbind(x,c(rep(0,i-1),rep(1,1),prev[a:b]))
  }
  x <- rbind(x,c(rep(0,length(n1)-1),rep(1,1)))
  return(x)
}
matfull4 <- function(n,prev)
{
  b <- 0
  x <- numeric()
  n1 <- which(grpnew==n)
  for(i in 1:(length(n1)-1))
  {
  
    a <- b+1
    
    b <- a+(length(n1)-i)-1
    
    x <- cbind(x,c(rep(0,i),prev[a:b]))
  }
  x <- cbind(x,c(rep(0,length(n1))))
  return(x)
}
        Y1 <- numeric()
        current11 <- numeric()
for(i in 1:ncol(val))
{
  current11[i] <- 1/var(val[,i])   #initial value of sigma
  Y1 <- c(Y1,val[,i]*as.numeric(sqrt(current11[i])))
}
  
X1 <- numeric()
for(i in 1:ncol(val))
{
  for(j in 1:ncol(val))
  {
    if(i < j)
    {
      aer <- c(rep(0,(i-1)*nrow(val)),val[,j]*as.numeric(sqrt(current11[j])),
                 rep(0,(j-i-1)*nrow(val)),val[,i]*as.numeric(sqrt(current11[i])),
                 rep(0,(ncol(val)-j)*nrow(val)))
        X1 <- cbind(X1,aer)
    }
    else
    {
      X1 <- X1
    }
  }
}
  

theta41 <- theta4(Y1,X1,gamma=gam)   #initial value of theta
  
while(distance > tol)
  {
    iter <- iter + 1
  
    previous <- current11
    prev <- theta41
    
    matnew <- matfull(prev)
    
    be <- matrix(-1,nrow(matnew),ncol(matnew))
    for(i in 1:nrow(matnew))
    {
      for(j in 1:ncol(matnew))
      {
        if(i<j)
        {
          be[i,j] <- matnew[i,j]*as.numeric(sqrt(previous[j]/previous[i]))
        }
        else if(i > j)
        {
          be[i,j] <- matnew[j,i]*as.numeric(sqrt(previous[j]/previous[i]))
        }
        else
        {
          be[i,j] <- -1
        }
      }
    
    }
    
    ben <- t(-be)
    for(i in 1:nrow(be))
    {
      sum <- 0
      for(j in 1:ncol(be))
      {
        if(j != i)
        {
          sum = sum+be[i,j]%*%val[,j]
        }
        else
          sum = sum
      }
      current11[i] <- nrow(val)/(norm(val[,i] - sum,"2"))^2
    }
    Y1 <- numeric()
    for(i in 1:ncol(val))
    {
      Y1 <- c(Y1,val[,i]*as.numeric(sqrt(current11[i])))
    }
    X1 <- numeric()
    for(i in 1:ncol(val))
    {
      for(j in 1:ncol(val))
      {
        if(i < j)
        {
          aer <- c(rep(0,(i-1)*nrow(val)),val[,j]*as.numeric(sqrt(current11[j])),
                   rep(0,(j-i-1)*nrow(val)),val[,i]*as.numeric(sqrt(current11[i])),
                   rep(0,(ncol(val)-j)*nrow(val)))
          X1 <- cbind(X1,aer)
        }
        else
        {
          X1 <- X1
        }
      }
    }
    theta41 <- theta4(Y1,X1,gamma=gam)
    distance <- norm(previous - current11,"2")
}
theta2[[n]] <- theta41
mat2[[n]] <- matfull3(n,theta2[[n]]) + matfull4(n,theta2[[n]])
  }
else
{
  theta2[[n]] <- 1
  mat2[[n]] <- as.matrix(1)
}

}

n <- numeric()
new <- list()
sum <- rep(0,c)
for(i in 1:c)
{
  n[i] <- length(which(grpnew==i))
  sum[i] <- sum[i] + sum(n[1:i])
}
  

new[[1]] <- cbind(mat2[[1]],matrix(0,n[1],p-n[1]))
for(i in 2:c)
{
new[[i]] <- cbind(matrix(0,n[i],sum[i-1]),mat2[[i]],matrix(0,n[i],p-sum[i-1]-n[i]))
  
}
omega11 <- numeric()
for(i in 1:c)
{
  omega11 <- rbind(omega11,new[[i]])
}

new2 <- numeric()
for(i in 1:c)
{
  new2 <- c(new2,rep(median(theta2[[i]]),ncol(mat2[[i]])))
}
omega21 <- diag(new2)

new3 <- numeric()
for(i in 1:c)
{
  new3 <- c(new3,median(theta2[[i]]))
}
omega31 <- diag(new3)

Sigmaest <-solve(omega11)

alphaf <- ((t(matrix(1,nrow(value),1))%*%omega11%*%matrix(1,nrow(value),1)))/p
wgtf <- (omega11%*%matrix(1,nrow(value),1))
weif <- wgtf/(p*as.numeric(alphaf))
Sigma1 <- matrix(0,p,p)
  for(i in 1:p)
  {
    for(j in 1:p)
    {
      Sigma1[i,j] <- 0.15^abs(i-j)
    }
  }
omegat <- solve(Sigma1)
alphat <- ((t(matrix(1,nrow(value),1))%*%omegat%*%matrix(1,nrow(value),1)))/p
wgtft <- (omegat%*%matrix(1,nrow(value),1))
weift <- wgtft/(p*as.numeric(alphat)) 


varest1 <- abs(((t(weif)%*%Sigmaest%*%weif)/(t(weift)%*%Sigma1%*%weift))-1)
varest1
#risk estimation error
riskest1 <- abs(t(weif)%*%(Sigmaest-Sigma1)%*%weif)
riskest1
#portfolio weight estimation error
portest1 <- norm(weift-weif,"1")
portest1

return(c(varest1,  portest1, riskest1))
#print("2nd type" : varest2, riskest2, portest2)

}
```
We run the above function for different values of gamma, the tuning parameter which returns the corresponding values of variance estimation error,portfolio weight estimation errorand  risk estimation error respectively .

Mu is 0 vector.

1. n = 100
   p = 50
   
   
```{r nex21}

n <- 100
p <- 50

set.seed(1)
mu <- rep(0,p)
value <- generate1(mu,n,p)
fviz_nbclust(scale(value), kmeans, method = "silhouette",k.max=40)
distnew <- diss(value,METHOD="PACF")     
hcnew <- hclust(distnew)
grpnew <- cutree(hcnew, k = 30)
table(grpnew)
c <- 30
newfunc(n,p,c,gamma=0.05)
newfunc(n,p,c,gamma=0.5)
newfunc(n,p,c,gamma=5)
newfunc(n,p,c,gamma=15)
newfunc(n,p,c,gamma=25)
newfunc(n,p,c,gamma=50)
```

2. n = 200
   p = 100

```{r next31}
n <- 200
p <- 100

set.seed(1)
mu <- rep(0,p)
value <- generate1(mu,n=200,p=100)
fviz_nbclust(scale(value), kmeans, method = "silhouette",k.max=30)
distnew <- diss(value,METHOD="PACF")     
hcnew <- hclust(distnew)
grpnew <- cutree(hcnew, k = 27)
table(grpnew)
c <- 27

newfunc(n,p,c,gamma=0.05)
newfunc(n,p,c,gamma=0.5)
newfunc(n,p,c,gamma=5)
newfunc(n,p,c,gamma=15)
newfunc(n,p,c,gamma=25)
newfunc(n,p,c,gamma=50)
```

3. n = 400
   p = 200
   
```{r next41}
n <- 400
p <- 200
set.seed(1)
mu <- rep(0,p)
value <- generate1(mu,n=400,p=200)
fviz_nbclust(scale(value), kmeans, method = "silhouette",k.max=50)
distnew <- diss(value,METHOD="PACF")     
hcnew <- hclust(distnew)
grpnew <- cutree(hcnew, k = 47)
table(grpnew)
c <- 47

newfunc(n,p,c,gamma=0.05)
newfunc(n,p,c,gamma=0.5)
newfunc(n,p,c,gamma=5)
newfunc(n,p,c,gamma=15)
newfunc(n,p,c,gamma=25)
newfunc(n,p,c,gamma=50)
```

4. n = 100
   p = 150
   
```{r next51}
n <- 100
p <- 150
set.seed(1)
mu <- rep(0,p)
value <- generate1(mu,n=100,p=150)
fviz_nbclust(scale(value), kmeans, method = "silhouette",k.max=40)
distnew <- diss(value,METHOD="PACF")     
hcnew <- hclust(distnew)
grpnew <- cutree(hcnew, k = 38)
table(grpnew)
c <- 38

newfunc(n,p,c,gamma=0.05)
newfunc(n,p,c,gamma=0.5)
newfunc(n,p,c,gamma=5)
newfunc(n,p,c,gamma=15)
newfunc(n,p,c,gamma=25)
newfunc(n,p,c,gamma=50)
```

5. n = 200
   p = 300
```{r next61}
n <- 200
p <- 300
set.seed(1)
mu <- rep(0,p)
value <- generate1(mu,n=200,p=300)
fviz_nbclust(scale(value), kmeans, method = "silhouette",k.max=60)
distnew <- diss(value,METHOD="PACF")     
hcnew <- hclust(distnew)
grpnew <- cutree(hcnew, k = 58)
table(grpnew)
c <- 58

newfunc(n,p,c,gamma=0.05)
newfunc(n,p,c,gamma=0.5)
newfunc(n,p,c,gamma=5)
newfunc(n,p,c,gamma=15)
newfunc(n,p,c,gamma=25)
newfunc(n,p,c,gamma=50)
```

6. n = 400
   p = 600
```{r next71}
n <- 400
p <- 600
set.seed(1)
mu <- rep(0,p)
value <- generate1(mu,n=400,p=600)

distnew <- diss(value,METHOD="PACF")     
hcnew <- hclust(distnew)
grpnew <- cutree(hcnew, k = 70)
table(grpnew)
c <- 70

newfunc(n,p,c,gamma=0.05)
newfunc(n,p,c,gamma=0.5)
newfunc(n,p,c,gamma=5)
newfunc(n,p,c,gamma=15)
newfunc(n,p,c,gamma=25)
newfunc(n,p,c,gamma=50)
```

Mu is generated from multivariate Normal(0,10^-4*I_p)

```{r nex11}
newfunc2 <- function(n,p,c,gamma)
{
   gam <- gamma
   theta2 <- list()
   mat2 <- list()
   for(n in 1:c)
   {
      n2 <- which(grpnew==n)
      if(length(n2) != 1)
      {
        tol <- 1e-5
        distance <- 1 + tol
        iter <- 0 

        value1 <- t(value) 
        val <- value1[,n2]
        matfull <- function(prev)
{
  b <- 0
  x <- numeric()
  for(i in 1:(ncol(val)-1))
  {
  
    a <- b+1
    
    b <- a+(ncol(val)-i)-1
    
    x <- rbind(x,c(rep(0,i-1),rep(1,1),prev[a:b]))
  }
  x <- rbind(x,c(rep(0,ncol(val)-1),rep(1,1)))
  return(x)
}
        Y1 <- numeric()
        current11 <- numeric()
for(i in 1:ncol(val))
{
  current11[i] <- 1/var(val[,i])   #initial value of sigma
  Y1 <- c(Y1,val[,i]*as.numeric(sqrt(current11[i])))
}
  
X1 <- numeric()
for(i in 1:ncol(val))
{
  for(j in 1:ncol(val))
  {
    if(i < j)
    {
      aer <- c(rep(0,(i-1)*nrow(val)),val[,j]*as.numeric(sqrt(current11[j])),
                 rep(0,(j-i-1)*nrow(val)),val[,i]*as.numeric(sqrt(current11[i])),
                 rep(0,(ncol(val)-j)*nrow(val)))
        X1 <- cbind(X1,aer)
    }
    else
    {
      X1 <- X1
    }
  }
}
  

theta41 <- theta4(Y1,X1,gamma=gam)   #initial value of theta
  
while(distance > tol)
  {
    iter <- iter + 1
  
    previous <- current11
    prev <- theta41
    
    matnew <- matfull(prev)
    
    be <- matrix(-1,nrow(matnew),ncol(matnew))
    for(i in 1:nrow(matnew))
    {
      for(j in 1:ncol(matnew))
      {
        if(i<j)
        {
          be[i,j] <- matnew[i,j]*as.numeric(sqrt(previous[j]/previous[i]))
        }
        else if(i > j)
        {
          be[i,j] <- matnew[j,i]*as.numeric(sqrt(previous[j]/previous[i]))
        }
        else
        {
          be[i,j] <- -1
        }
      }
    
    }
    
    ben <- t(-be)
    for(i in 1:nrow(be))
    {
      sum <- 0
      for(j in 1:ncol(be))
      {
        if(j != i)
        {
          sum = sum+be[i,j]%*%val[,j]
        }
        else
          sum = sum
      }
      current11[i] <- nrow(val)/(norm(val[,i] - sum,"2"))^2
    }
    Y1 <- numeric()
    for(i in 1:ncol(val))
    {
      Y1 <- c(Y1,val[,i]*as.numeric(sqrt(current11[i])))
    }
    X1 <- numeric()
    for(i in 1:ncol(val))
    {
      for(j in 1:ncol(val))
      {
        if(i < j)
        {
          aer <- c(rep(0,(i-1)*nrow(val)),val[,j]*as.numeric(sqrt(current11[j])),
                   rep(0,(j-i-1)*nrow(val)),val[,i]*as.numeric(sqrt(current11[i])),
                   rep(0,(ncol(val)-j)*nrow(val)))
          X1 <- cbind(X1,aer)
        }
        else
        {
          X1 <- X1
        }
      }
    }
    theta41 <- theta4(Y1,X1,gamma=gam)
    distance <- norm(previous - current11,"2")
}
theta2[[n]] <- theta41
mat2[[n]] <- matfull3(n,theta2[[n]]) + matfull4(n,theta2[[n]])
  }
else
{
  theta2[[n]] <- 1
  mat2[[n]] <- as.matrix(1)
}

}

n <- numeric()
new <- list()
sum <- rep(0,c)
for(i in 1:c)
{
  n[i] <- length(which(grpnew==i))
  sum[i] <- sum[i] + sum(n[1:i])
}
  

new[[1]] <- cbind(mat2[[1]],matrix(0,n[1],p-n[1]))
for(i in 2:c)
{
new[[i]] <- cbind(matrix(0,n[i],sum[i-1]),mat2[[i]],matrix(0,n[i],p-sum[i-1]-n[i]))
  
}
omega11 <- numeric()
for(i in 1:c)
{
  omega11 <- rbind(omega11,new[[i]])
}

new2 <- numeric()
for(i in 1:c)
{
  new2 <- c(new2,rep(median(theta2[[i]]),ncol(mat2[[i]])))
}
omega21 <- diag(new2)

new3 <- numeric()
for(i in 1:c)
{
  new3 <- c(new3,median(theta2[[i]]))
}
omega31 <- diag(new3)

Sigmaest <-solve(omega11)

mustar <- 0.000376
alphaf <- as.numeric(((t(matrix(1,nrow(value),1))%*%omega11%*%matrix(1,nrow(value),1)))/p)
betaf <- as.numeric(((t(matrix(1,nrow(value),1))%*%omega11%*%as.matrix(mu)))/p)
deltaf <- as.numeric((t(as.matrix(mu))%*%omega11%*%(as.matrix(mu)))/p)
wgtf1 <- (omega11%*%matrix(1,nrow(value),1))
wgtf2 <- (omega11%*%as.matrix(mu))
weif <- (wgtf1*((deltaf-(mustar*betaf))/(p*((alphaf*deltaf)-(betaf^2)))))+
        (wgtf2*(((alphaf*mustar)-betaf)/(p*((alphaf*deltaf)-(betaf^2)))))

#alphaf1 <- as.numeric(((t(matrix(1,nrow(value),1))%*%omega21%*%matrix(1,nrow(value),1)))/p)
#betaf1 <- as.numeric(((t(matrix(1,nrow(value),1))%*%omega21%*%as.matrix(mu)))/p)
#deltaf1 <- as.numeric((t(as.matrix(mu))%*%omega21%*%(as.matrix(mu)))/p)
#wgtf11 <- (omega21%*%matrix(1,nrow(value),1))
#wgtf21 <- (omega21%*%as.matrix(mu))
#weif1 <- (wgtf11*((deltaf1-(mustar*betaf1))/(p*((alphaf1*deltaf1)-(betaf1^2)))))+
#        (wgtf21*(((alphaf1*mustar)-betaf1)/(p*((alphaf1*deltaf1)-(betaf1^2)))))

Sigma1 <- matrix(0,p,p)
  for(i in 1:p)
  {
    for(j in 1:p)
    {
      Sigma1[i,j] <- 0.15^abs(i-j)
    }
  }
omegat <- solve(Sigma1)
alphaft <- as.numeric(((t(matrix(1,nrow(value),1))%*%omegat%*%matrix(1,nrow(value),1)))/p)
betaft <- as.numeric(((t(matrix(1,nrow(value),1))%*%omegat%*%as.matrix(mu)))/p)
deltaft <- as.numeric((t(as.matrix(mu))%*%omegat%*%(as.matrix(mu)))/p)
wgtft1 <- (omegat%*%matrix(1,nrow(value),1))
wgtft2 <- (omegat%*%as.matrix(mu))
weift <- (wgtft1*((deltaft-(mustar*betaft))/(p*((alphaft*deltaft)-(betaft^2)))))+
        (wgtft2*(((alphaft*mustar)-betaft)/(p*((alphaft*deltaft)-(betaft^2)))))

varest1 <- abs(((t(weif)%*%Sigmaest%*%weif)/(t(weift)%*%Sigma1%*%weift))-1)

#risk estimation error
riskest1 <- abs(t(weif)%*%(Sigmaest-Sigma1)%*%weif)

#portfolio weight estimation error
portest1 <- norm(weift-weif,"1")


#varest2 <- abs(((t(weif1)%*%Sigmaest2%*%weif1)/(t(weift)%*%Sigma1%*%weift))-1)

#risk estimation error
#riskest2 <- print("Not possible")

#portfolio weight estimation error
#portest2 <- norm(weift-weif2,"1")


return(c(varest1,  portest1, riskest1))
#print("2nd type" : varest2, riskest2, portest2)

}
```

1. n = 100
   p = 50
   
   
```{r next2}
n <- 100
p <- 50
set.seed(1)
mu <- mvrnorm(1,rep(0,50),1e-4*diag(1,50))
value <- generate1(mu,n=100,p=50)
fviz_nbclust(scale(value), kmeans, method = "silhouette",k.max=20)
distnew <- diss(value,METHOD="PACF")     
hcnew <- hclust(distnew)
grpnew <- cutree(hcnew, k = 15)
table(grpnew)
c <- 15

newfunc2(n,p,c,gamma=0.05)
newfunc2(n,p,c,gamma=0.5)
newfunc2(n,p,c,gamma=5)
newfunc2(n,p,c,gamma=15)
newfunc2(n,p,c,gamma=25)
newfunc2(n,p,c,gamma=50)
```

2. n = 200
   p = 100

```{r next3}
set.seed(1)
mu <- mvrnorm(1,rep(0,100),1e-4*diag(1,100))
value <- generate1(mu,n=200,p=100)
fviz_nbclust(scale(value), kmeans, method = "silhouette",k.max=40)
distnew <- diss(value,METHOD="PACF")     
hcnew <- hclust(distnew)
grpnew <- cutree(hcnew, k = 32)
table(grpnew)

n <- 200
p <- 100
c <- 32

newfunc2(n,p,c,gamma=0.05)
newfunc2(n,p,c,gamma=0.5)
newfunc2(n,p,c,gamma=5)
newfunc2(n,p,c,gamma=15)
newfunc2(n,p,c,gamma=25)
newfunc2(n,p,c,gamma=50)
```

3. n = 400
   p = 200
   
```{r next4}
set.seed(1)
mu <- mvrnorm(1,rep(0,200),1e-4*diag(1,200))
value <- generate1(mu,n=400,p=200)
fviz_nbclust(scale(value), kmeans, method = "silhouette",k.max=50)
distnew <- diss(value,METHOD="PACF")     
hcnew <- hclust(distnew)
grpnew <- cutree(hcnew, k = 50)
table(grpnew)

n <- 400
p <- 200
c <- 50

newfunc2(n,p,c,gamma=0.05)
newfunc2(n,p,c,gamma=0.5)
newfunc2(n,p,c,gamma=5)
newfunc2(n,p,c,gamma=15)
newfunc2(n,p,c,gamma=25)
newfunc2(n,p,c,gamma=50)
```

4. n = 100
   p = 150
   
```{r next5}
set.seed(1)
mu <- mvrnorm(1,rep(0,150),1e-4*diag(1,150))
value <- generate1(mu,n=100,p=150)
fviz_nbclust(scale(value), kmeans, method = "silhouette",k.max=40)
distnew <- diss(value,METHOD="PACF")     
hcnew <- hclust(distnew)
grpnew <- cutree(hcnew, k = 40)
table(grpnew)

n <- 100
p <- 150
c <- 40

newfunc2(n,p,c,gamma=0.05)
newfunc2(n,p,c,gamma=0.5)
newfunc2(n,p,c,gamma=5)
newfunc2(n,p,c,gamma=15)
newfunc2(n,p,c,gamma=25)
newfunc2(n,p,c,gamma=50)
```

5. n = 200
   p = 300
```{r next6}
set.seed(1)
mu <- mvrnorm(1,rep(0,300),1e-4*diag(1,300))
value <- generate1(mu,n=200,p=300)
fviz_nbclust(scale(value), kmeans, method = "silhouette",k.max=50)
distnew <- diss(value,METHOD="PACF")     
hcnew <- hclust(distnew)
grpnew <- cutree(hcnew, k = 50)
table(grpnew)

n <- 200
p <- 300
c <- 50

newfunc2(n,p,c,gamma=0.05)
newfunc2(n,p,c,gamma=0.5)
newfunc2(n,p,c,gamma=5)
newfunc2(n,p,c,gamma=15)
newfunc2(n,p,c,gamma=25)
newfunc2(n,p,c,gamma=50)
```

6. n = 400
   p = 600
```{r next7}
set.seed(1)
mu <- mvrnorm(1,rep(0,600),1e-4*diag(1,600))
value <- generate1(mu,n=400,p=600)

distnew <- diss(value,METHOD="PACF")     
hcnew <- hclust(distnew)
grpnew <- cutree(hcnew, k = 70)
table(grpnew)

n <- 400
p <- 600
c <- 70

newfunc2(n,p,c,gamma=0.05)
newfunc2(n,p,c,gamma=0.5)
newfunc2(n,p,c,gamma=5)
newfunc2(n,p,c,gamma=15)
newfunc2(n,p,c,gamma=25)
newfunc2(n,p,c,gamma=50)
```